Lesson 4
========================================================

```{r}

getwd()
setwd('C:/Users/Administrator/Desktop/R/EDA_Course_Materials/lesson3')
list.files() #列出目录中的文件
df <- read.csv('pseudo_facebook.tsv', sep = "\t")
# df <- read.delim('pseudo_facebook.tsv')
names(df)

```


***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
library(ggplot2)
str(df)

p1 <- qplot(data = df, x = age, y = friend_count)
ggplot(data = df, aes(x = age, y = friend_count)) +
  geom_point() +
  scale_x_continuous(breaks = seq(0,120,10))

summary(df$age)

p1 + xlim(13,90)

ggplot(data = df, aes(x = age, y = friend_count)) +
  geom_point(alpha = 1/20) +
  xlim(13,90)


ggplot(data = df, aes(x = age, y = friend_count)) +  #geom_point(position = "jitter").  
  geom_jitter(alpha = 1/20) +
  xlim(13,90)

ggplot(data = df, aes(x = age, y = friend_count)) +  #geom_point(position = "jitter").  
  geom_jitter(alpha = 1/20) +
  xlim(13,90) +
  scale_y_log10()

ggplot(data = df, aes(x = age, y = friend_count)) +  #geom_point(position = "jitter").  
  geom_point(alpha = 1/20, position = position_jitter(height = 0)) +
  xlim(13,90) +  
  coord_trans(y = 'sqrt')

ggplot(data = df, aes(x = age, y = friend_count)) +  #geom_point(position = "jitter").  
  geom_jitter(alpha = 1/20) +
  xlim(13,90) +
  scale_y_sqrt()




```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(data = df, aes(x = age, y = friend_count)) +
  geom_point() +
  scale_x_continuous(breaks = seq(0,120,10))
```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(data = df, aes(x = age, y = friend_count)) +
  geom_point(alpha = 1/20) +
  xlim(13,90)
```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}
ggplot(data = df, aes(x = age, y = friend_count)) +  #geom_point(position = "jitter").  
  geom_point(alpha = 1/20, position = position_jitter(height = 0)) +
  xlim(13,90) +  
  coord_trans(y = 'sqrt')

ggplot(data = df, aes(x = age, y = friend_count)) +  #geom_point(position = "jitter").  
  geom_jitter(alpha = 1/20) +
  xlim(13,90) +
  scale_y_sqrt()
```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}
ggplot(data = df, aes(x = age, y = friend_count)) +  #geom_point(position = "jitter").  
  geom_point(alpha = 1/20, position = position_jitter(height = 0)) +
  xlim(13,90) +  
  coord_trans(y = 'sqrt')

ggplot(data = df, aes(x = age, y = friend_count)) +  #geom_point(position = "jitter").  
  geom_jitter(alpha = 1/20) +
  xlim(13,90) +
  scale_y_sqrt()
```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(data = df, aes(x = age, y = friendships_initiated)) +
  geom_jitter()

# 加入coord_trans(y = 'sqrt') 时出现Error in if (zero_range(range)) { : missing value where TRUE/FALSE neededyo
#错误是因为有一些数据是0，使用噪音取该数字的平方根时他可能是负数，结果会出现虚数
#这时需要将position = 'jitter'改为：

# ggplot(data = df, aes(x = age, y = friendships_initiated)) +
#   geom_point(alpha = 1/20, position = 'jitter') +
#   scale_x_continuous(limits = c(1,90), breaks = seq(1,90, 10)) +
#   coord_trans(y = 'sqrt')

ggplot(data = df, aes(x = age, y = friendships_initiated)) +
  geom_point(alpha = 1/20, position = position_jitter(height = 0)) +
  scale_x_continuous(limits = c(1,90), breaks = seq(1,90, 10)) +
  coord_trans(y = 'sqrt')
  

```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
# install.packages('dplyr')
library('dplyr')
library('tidyr')

# age_group <- group_by(df, age)
# df.fc_by_age <- summarise(age_group, 
#           friend_count_mean = mean(friend_count),
#           friend_count_median = median(friend_count),
#           n = n())
# 
# #sort data by age
# df.fc_by_age <- arrange(.data = df.fc_by_age,... = age)


df.fc_by_age <- df %>%
  group_by(age) %>%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>%
  arrange(age)

head(df.fc_by_age)

```

Create your plot!
注意：ggplot 2.0.0 在使用 stat = 'summary' 时改变了函数“参数自变量”的语法。要表示在 fun.y 指定的函数上设置的参数，请使用 fun.args 参数，比如 
geom_line(stat = 'summary', fun.y = quantile, fun.args = list(probs = .9), ... )

```{r Conditional Means Plot}
names(df.fc_by_age)
ggplot(data = df.fc_by_age, aes(x = age, y = friend_count_mean)) +
  geom_point(color = 'green') +
  geom_line()


```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}

ggplot(data = df, aes(x = age, y = friend_count)) + 
  geom_point(alpha = 1/20, 
             position = position_jitter(height = 0),
             color = 'orange') +
  xlim(13,90) +
  coord_trans(y = 'sqrt') + 
  geom_line(stat = 'summary', fun.y = mean) +
  geom_line(stat = 'summary', fun.y = quantile, fun.args = 0.1,
            color = 'blue', linetype = 2) +
  geom_line(stat = 'summary', fun.y = quantile, fun.args = 0.9,
            color = 'blue', linetype = 2) +
  geom_line(stat = 'summary', fun.y = quantile, fun.args = 0.5,
            color = 'blue', linetype = 2)


ggplot(data = df, aes(x = age, y = friend_count)) + 
  geom_point(alpha = 1/20, 
             position = position_jitter(height = 0),
             color = 'orange') +
  coord_cartesian(xlim = c(13, 90), ylim = c(0, 1000)) +
  geom_line(stat = 'summary', fun.y = mean) +
  geom_line(stat = 'summary', fun.y = quantile, fun.args = 0.1,
            color = 'blue', linetype = 2) +
  geom_line(stat = 'summary', fun.y = quantile, fun.args = 0.9,
            color = 'blue', linetype = 2) +
  geom_line(stat = 'summary', fun.y = quantile, fun.args = 0.5,
            color = 'blue', linetype = 2)


```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:根据经验相关系数大于0.3或者小于-0.3表示有意义但较小；在0.5-0.7或者以上表示很大关系

```{r Correlation}
cor.test(x = df$age, y = df$friend_count, method = 'pearson')

with(data = df, expr = cor.test(x = age, y = friend_count, method = 'pearson'))





```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(data = subset(df, age <= 70), cor.test(age, friend_count)) #默认使用Pearson

# with(data = subset(df, age <= 70), cor.test(age, friend_count, method = 'kendall'))

with(data = subset(df, age <= 70), cor.test(age, friend_count, method = 'spearman')) 


```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}
ggplot(data = df, aes(x = www_likes_received, y = likes_received)) +
  geom_point()

```

***

### Strong Correlations
Notes:放大图像，抽象出重要规律

```{r Strong Correlations}
ggplot(data = df, aes(x = www_likes_received, y = likes_received)) +
  geom_point() +
  coord_cartesian(xlim = c(0,quantile(df$www_likes_received, 0.95)), 
                  ylim = c(0, quantile(df$likes_received, 0.95))) +
  geom_smooth(method = 'lm', color = 'red')

ggplot(data = df, aes(x = www_likes_received, y = likes_received)) +
  geom_point() +
  ylim(0,quantile(df$likes_received, 0.95)) + 
  xlim(0,quantile(df$www_likes_received, 0.95)) +
  geom_smooth(method = 'lm', color = 'red')

```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}
cor.test(df$www_likes_received, df$likes_received)



```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
# install.packages('alr3')
library(alr3)
data("Mitchell")


```

Create your plot!

```{r Temp vs Month}
str(Mitchell)
ggplot(data = Mitchell, aes(x = Month, y = Temp)) + 
  geom_point()
```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.
0.01

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}

cor.test(Mitchell$Month, Mitchell$Temp)


```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}
ggplot(data = Mitchell, aes(x = Month, y = Temp)) + 
  geom_point() +
  scale_x_continuous(breaks = seq(0,12,1), limits = c(0,12))

ggplot(data = Mitchell, aes(x = Month, y = Temp)) + 
  geom_point() +
  scale_x_continuous(breaks = seq(0,203,12))

ggplot(data = Mitchell, aes(x = (Month%%12), y = Temp)) +
  geom_point() +
  geom_line(stat = 'summary', fun.y = mean, color = 'red')


# install.packages("energy")
library(energy)

cor.test(Mitchell$Month, Mitchell$Temp)
dcor.ttest(Mitchell$Month, Mitchell$Temp)


```

energy 包中的 dcor.ttest() 函数对两个变量的独立性执行非参数检验。尽管 Mitchell 土壤数据集太过粗糙，以至于无法识别“月份”和“温度”之间的显著依赖性。我们可以通过其他例子了解 dcor.ttest 和 cor.test 的区别，例如：
```{r}
x <- seq(0, 4*pi, pi/20)
y <- cos(x)
qplot(x = x, y = y)
dcor.ttest(x, y)
cor.test(x,y)
```





***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}

```

***

### Age with Months Means

```{r Age with Months Means}
df$age_with_months <- df$age + (1 - df$dob_month / 12)
df$age_with_months <- with(df, age + (1 - dob_month / 12))

```

Programming Assignment
```{r Programming Assignment}
df.fc_by_age_months <- df %>%
  group_by(age_with_months) %>%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>%
  arrange(age_with_months)




```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}
p1 <- ggplot(data = subset(df.fc_by_age_months, age_with_months<=71), 
             aes(x = age_with_months, y = friend_count_mean)) +
  geom_line() +
  geom_smooth()


p2 <-  ggplot(data = subset(df.fc_by_age, age<=71), aes(x = age, y = friend_count_mean)) +
  geom_line() +
  geom_smooth()


ggplot(data = subset(df.fc_by_age_months, age_with_months<=71), aes(x = age_with_months, y = friend_count_mean)) +
  geom_point() +
  geom_line(stat = 'summary', fun.y = mean, color = 'red')

p3 <- ggplot(data = subset(df, age<=71), aes(x = round(age / 5) * 5, y = friend_count)) +
  geom_line(stat = 'summary', fun.y = mean, color = 'red')


library(gridExtra)
grid.arrange(p1, p2, p3, ncol = 1)



```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

