Lesson 3
========================================================

***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
getwd()
setwd('C:/Users/Administrator/Desktop/R/EDA_Course_Materials/lesson3')
list.files() #列出目录中的文件
df <- read.csv('pseudo_facebook.tsv', sep = "\t")
names(df)
```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
# install.packages('ggplot2')
library(ggplot2)

qplot(data = df,x = dob_day) + 
  scale_x_continuous(breaks = 1:31)
  # scale_x_discrete(breaks=1:31)




```

***

#### What are some things that you notice about this histogram?
Response:注册帐号时，很多网站会将你的生日默认为1号，甚至1月1号。对于 Facebook，他们的默认是1月1日。

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}
qplot(data = df, x = dob_day) + 
  scale_x_continuous(breaks = 1:31) +
  facet_wrap(~dob_month, nrow = 3)
  # facet_grid()

```

#### Lets take another look at our plot. What stands out to you here?
Response:

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moiras outlier?
Response:

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
ggplot(data = df, aes(x = friend_count)) +
  geom_histogram()

qplot(data = df, x = friend_count)





```

#### How is this plot similar to Moira's first plot?
Response:

***

### Limiting the Axes
Notes:

```{r Limiting the Axes}
ggplot(data = df, aes(x = friend_count)) +
  geom_histogram()

qplot(data = df, x = friend_count, xlim = c(0, 1000))

qplot(data = df, x = friend_count, binwidth = 25) + 
  scale_x_continuous(limits = c(0, 1000), 
                     breaks = seq(0, 1000, 50))
```

### Exploring with Bin Width
Notes:

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = df, binwidth = 20) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}
qplot(data = subset(df, !is.na(gender)), x = friend_count, binwidth = 20) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)

qplot(data = na.omit(df), x = friend_count, binwidth = 20) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)     #na.omit会省略所有含有na的行,不光对于gender

```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
table(df$gender)
by(df$friend_count, df$gender, summary) #注意中位数小于均值（因为数据是长尾分布）中位数比均值更加稳健


```

#### Who on average has more friends: men or women?
Response:

#### What's the difference between the median friend count for women and men?
Response:

#### Why would the median be a better measure than the mean?
Response:

***

### Tenure
参数 color 决定了图中对象的轮廓线颜色（color outline）。 
参数 fill 决定了图中对象内的区域（area）颜色。 
你可能注意到颜色 black 和十六进制代码的颜色 #099DD9（一种蓝色阴影）如何封装在 I() 内。I() 函数代表“现状”，并且告诉 qplot 将它们用作颜色。 

等效的 ggplot 语法： 
ggplot(aes(x = tenure), data = pf) + 
   geom_histogram(binwidth = 30, color = 'black', fill = '#099DD9')

等效的 ggplot 语法： 
ggplot(aes(x = tenure/365), data = pf) + 
   geom_histogram(binwidth = .25, color = 'black', fill = '#F79420')

Notes:

```{r Tenure}
qplot(data = df, x = tenure, binwidth = 30, 
      color = I('black'), fill = I('#099DD9'))




```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
qplot(data = df, x = tenure/365, binwidth = .25, 
      color = I('black'), fill = I('#F79420')) +
  scale_x_continuous(limits = c(0,7), breaks = seq(1,7,1))

```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
Lesson 3
========================================================

***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
getwd()
setwd('C:/Users/Administrator/Desktop/R/EDA_Course_Materials/lesson3')
list.files() #列出目录中的文件
df <- read.csv('pseudo_facebook.tsv', sep = "\t")
names(df)
```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
# install.packages('ggplot2')
library(ggplot2)

qplot(data = df,x = dob_day) + 
  scale_x_continuous(breaks = 1:31)
  # scale_x_discrete(breaks=1:31)




```

***

#### What are some things that you notice about this histogram?
Response:注册帐号时，很多网站会将你的生日默认为1号，甚至1月1号。对于 Facebook，他们的默认是1月1日。

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}
qplot(data = df, x = dob_day) + 
  scale_x_continuous(breaks = 1:31) +
  facet_wrap(~dob_month, nrow = 3)
  # facet_grid()

```

#### Lets take another look at our plot. What stands out to you here?
Response:

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moiras outlier?
Response:

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
ggplot(data = df, aes(x = friend_count)) +
  geom_histogram()

qplot(data = df, x = friend_count)





```

#### How is this plot similar to Moira's first plot?
Response:

***

### Limiting the Axes
Notes:

```{r Limiting the Axes}
ggplot(data = df, aes(x = friend_count)) +
  geom_histogram()

qplot(data = df, x = friend_count, xlim = c(0, 1000))

qplot(data = df, x = friend_count, binwidth = 25) + 
  scale_x_continuous(limits = c(0, 1000), 
                     breaks = seq(0, 1000, 50))
```

### Exploring with Bin Width
Notes:

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = df, binwidth = 20) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}
qplot(data = subset(df, !is.na(gender)), x = friend_count, binwidth = 20) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)

qplot(data = na.omit(df), x = friend_count, binwidth = 20) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)     #na.omit会省略所有含有na的行,不光对于gender

```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
table(df$gender)
by(df$friend_count, df$gender, summary) #注意中位数小于均值（因为数据是长尾分布）中位数比均值更加稳健


```

#### Who on average has more friends: men or women?
Response:

#### What's the difference between the median friend count for women and men?
Response:

#### Why would the median be a better measure than the mean?
Response:

***

### Tenure
参数 color 决定了图中对象的轮廓线颜色（color outline）。 
参数 fill 决定了图中对象内的区域（area）颜色。 
你可能注意到颜色 black 和十六进制代码的颜色 #099DD9（一种蓝色阴影）如何封装在 I() 内。I() 函数代表“现状”，并且告诉 qplot 将它们用作颜色。 

等效的 ggplot 语法： 
ggplot(aes(x = tenure), data = pf) + 
   geom_histogram(binwidth = 30, color = 'black', fill = '#099DD9')

等效的 ggplot 语法： 
ggplot(aes(x = tenure/365), data = pf) + 
   geom_histogram(binwidth = .25, color = 'black', fill = '#F79420')

Notes:

```{r Tenure}
qplot(data = df, x = tenure, binwidth = 30, 
      color = I('black'), fill = I('#099DD9'))




```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
qplot(data = df, x = tenure/365, binwidth = .25, 
      color = I('black'), fill = I('#F79420'), xlab = 'x', ylab = 'y') +
  scale_x_continuous(limits = c(0,7), breaks = seq(1,7,1))

```

***

### Labeling Plots
Notes:

```{r Labeling Plots}

Lesson 3
========================================================

***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
getwd()
setwd('C:/Users/Administrator/Desktop/R/EDA_Course_Materials/lesson3')
list.files() #列出目录中的文件
df <- read.csv('pseudo_facebook.tsv', sep = "\t")
names(df)
```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
# install.packages('ggplot2')
library(ggplot2)

qplot(data = df,x = dob_day) + 
  scale_x_continuous(breaks = 1:31)
  # scale_x_discrete(breaks=1:31)




```

***

#### What are some things that you notice about this histogram?
Response:注册帐号时，很多网站会将你的生日默认为1号，甚至1月1号。对于 Facebook，他们的默认是1月1日。

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}
qplot(data = df, x = dob_day) + 
  scale_x_continuous(breaks = 1:31) +
  facet_wrap(~dob_month, nrow = 3)
  # facet_grid()

```

#### Lets take another look at our plot. What stands out to you here?
Response:

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moiras outlier?
Response:

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
ggplot(data = df, aes(x = friend_count)) +
  geom_histogram()

qplot(data = df, x = friend_count)





```

#### How is this plot similar to Moira's first plot?
Response:

***

### Limiting the Axes
Notes:

```{r Limiting the Axes}
ggplot(data = df, aes(x = friend_count)) +
  geom_histogram()

qplot(data = df, x = friend_count, xlim = c(0, 1000))

qplot(data = df, x = friend_count, binwidth = 25) + 
  scale_x_continuous(limits = c(0, 1000), 
                     breaks = seq(0, 1000, 50))
```

### Exploring with Bin Width
Notes:

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = df, binwidth = 20) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}
qplot(data = subset(df, !is.na(gender)), x = friend_count, binwidth = 20) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)

qplot(data = na.omit(df), x = friend_count, binwidth = 20) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)     #na.omit会省略所有含有na的行,不光对于gender

```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
table(df$gender)
by(df$friend_count, df$gender, summary) #注意中位数小于均值（因为数据是长尾分布）中位数比均值更加稳健


```

#### Who on average has more friends: men or women?
Response:

#### What's the difference between the median friend count for women and men?
Response:

#### Why would the median be a better measure than the mean?
Response:

***

### Tenure
参数 color 决定了图中对象的轮廓线颜色（color outline）。 
参数 fill 决定了图中对象内的区域（area）颜色。 
你可能注意到颜色 black 和十六进制代码的颜色 #099DD9（一种蓝色阴影）如何封装在 I() 内。I() 函数代表“现状”，并且告诉 qplot 将它们用作颜色。 

等效的 ggplot 语法： 
ggplot(aes(x = tenure), data = pf) + 
   geom_histogram(binwidth = 30, color = 'black', fill = '#099DD9')

等效的 ggplot 语法： 
ggplot(aes(x = tenure/365), data = pf) + 
   geom_histogram(binwidth = .25, color = 'black', fill = '#F79420')

Notes:

```{r Tenure}
qplot(data = df, x = tenure, binwidth = 30, 
      color = I('black'), fill = I('#099DD9'))




```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
qplot(data = df, x = tenure/365, binwidth = .25, 
      color = I('black'), fill = I('#F79420'), xlab = 'x', ylab = 'y') +
  scale_x_continuous(limits = c(0,7), breaks = seq(1,7,1))

```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
qplot(data = df, x = tenure/365, binwidth = .25, 
      color = I('black'), fill = I('#F79420')) +
  scale_x_continuous(limits = c(0,7), breaks = seq(1,7,1))

```

***

### User Ages
Notes:

```{r User Ages}
qplot(data = df, x = age, binwidth = 1,
      color = I('black'), fill = I('#5760AB'), 
      xlab = 'x', ylab = 'y') +
  scale_x_continuous(limits = c(1, 120), breaks = seq(0,113,5))

summary(df$age)

```

#### What do you notice?
Response:

***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:

***

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}
p1 <- qplot(data = df, x = friend_count)

summary(df$friend_count)

summary(log10(df$friend_count +1)) #取log变换消除长尾

qplot(x = log10(df$friend_count +1))
p2 <- p1 + 
  scale_x_log10()


qplot(x = sqrt(df$friend_count +1))
p3 <- p1 + 
  scale_x_sqrt()


# install.packages("gridExtra") #一个图像框内创建多个图
library(gridExtra)

grid.arrange(p1, p2, p3, ncol=1)


p4 <- ggplot(aes(x = friend_count), data = df) +
  geom_histogram()

p5 <- ggplot(aes(x = friend_count), data = df) +
  geom_histogram() +
  scale_x_log10()

p6 <- ggplot(aes(x = friend_count), data = df) +
  geom_histogram() +
  scale_x_sqrt()

grid.arrange(p4, p5, p6, ncol=1)

ggplot(aes(x = friend_count), data = df) +
  geom_density()


```

***
请注意，sum(..count..) 将跨颜色进行总计，因此，显示的百分比是总用户数的百分比。要在每个组内绘制百分比，你可以尝试
y = ..density...
请注意，频率多边形的形状取决于我们如何设置箱子――在个别直方图中，线条的高度与条形的高度相同，但线条更容易进行比较，因为它们都在同一轴上。

### Frequency Polygons

```{r Frequency Polygons}
ggplot(aes(x = friend_count, y = ..count../sum(..count..)), 
       data = subset(df, !is.na(gender))) + 
  geom_freqpoly(aes(color = gender), binwidth=10) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  xlab('好友数量') + 
  ylab('Percentage of users with that friend count')


qplot(data = subset(df, !is.na(df$gender)), x = friend_count,
      binwidth=10) +
  scale_x_continuous(limits = c(0,1000), breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)


qplot(data = subset(df, !is.na(df$gender)), x = friend_count, 
      binwidth=10, color = gender) +
  scale_x_continuous(limits = c(0,1000), breaks = seq(0, 1000, 50))

##########################################################################

qplot(data = subset(df, !is.na(df$gender)), x = friend_count, 
      y =..count../sum(..count..),
      binwidth = 10, color = gender, geom = 'freqpoly',
      xlab = '好友数量', 
      ylab = 'Percentage of users with that friend count') +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))


qplot(data = subset(df, !is.na(df$gender)), x = friend_count, y = ..density..,
      binwidth = 10, color = gender, geom = 'freqpoly',
      xlab = '好友数量', 
      ylab = 'Percentage of users with that friend count') +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))

##########################################################################

qplot(data = subset(df, !is.na(df$gender)), x = friend_count, 
      y =..count../sum(..count..),
      binwidth = 5, color = gender, geom = 'freqpoly',
      xlab = '好友数量', 
      ylab = 'Percentage of users with that friend count') +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))


qplot(data = subset(df, !is.na(df$gender)), x = friend_count, y = ..density..,
      binwidth = 5, color = gender, geom = 'freqpoly',
      xlab = '好友数量', 
      ylab = 'Percentage of users with that friend count') +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))




```

***

### Likes on the Web
Notes:

```{r Likes on the Web}
by(df$www_likes, df$gender, summary)

by(df$www_likes, df$gender, sum) # 用sum函数对www_likes字段通过gender分组统计



```


***

### Box Plots
Notes:

```{r Box Plots}
qplot(data = subset(df, !is.na(df$gender)), geom = 'boxplot', 
      y = friend_count, x = gender)

qplot(data = subset(df, !is.na(df$gender)), geom = 'boxplot', 
      y = friend_count, x = gender, ylim = c(0, 1000))

qplot(data = subset(df, !is.na(df$gender)), geom = 'boxplot', 
      y = friend_count, x = gender) + 
  scale_y_continuous(limits = c(0, 1000))

qplot(data = subset(df, !is.na(df$gender)), geom = 'boxplot', 
      y = friend_count, x = gender) + 
  coord_cartesian(ylim = c(0, 1000))

by(df$friend_count, df$gender, summary)


#对比下面两个图可以发现当在qplot中使用ylim时，变换不同的ylim将得到数据的不同变换
#与我们的数据不符，在coord_cartesian中使用会得到数据相符的不同的图像
qplot(data = subset(df, !is.na(df$gender)), geom = 'boxplot', 
      y = friend_count, x = gender) + 
  coord_cartesian(ylim = c(0, 250))

qplot(data = subset(df, !is.na(df$gender)), geom = 'boxplot', 
      y = friend_count, x = gender) + 
  scale_y_continuous(limits = c(0, 250))





```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}

```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}
by(df$friendships_initiated, df$gender, summary)

qplot(data = subset(df, !is.na(df$gender)), y = friendships_initiated, x = gender,
      geom = 'boxplot') + 
  coord_cartesian(ylim = c(0, 150))


```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}

```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}
summary(df$www_likes)

summary(df$www_likes > 0)

df$mobile_check_in <- NA  
df$mobile_check_in <- ifelse(df$mobile_likes > 0, 1, 0)
df$mobile_check_in <- factor(df$mobile_check_in)
summary(df$mobile_check_in)

```

Response:

***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!




