Lesson 5
========================================================

### Multivariate Data
Notes:

***

### Moira Perceived Audience Size Colored by Age
Notes:

***

### Third Qualitative Variable
Notes:

```{r Third Qualitative Variable}
library(dplyr)
library(ggplot2)
getwd()
setwd('C:/Users/Administrator/Desktop/R/EDA_Course_Materials/lesson3')
list.files()
df <- read.delim("pseudo_facebook.tsv")


ggplot(aes(x = age),data = subset(df, !is.na(gender))) + 
  geom_histogram() +
  facet_wrap(~gender)


ggplot(aes(x = gender, y = age),data = subset(df, !is.na(gender))) + 
  geom_boxplot() +
  stat_summary(fun.y = mean, geom = 'point', shape = 4)


ggplot(aes(x = age, y = friend_count),
       data = subset(df, !is.na(gender))) + 
  geom_line(aes(color = gender), stat = 'summary', fun.y = median)
  

df.df_by_age_gender <- df %>%
  filter(!is.na(gender)) %>%
  group_by(age, gender) %>%
  summarise(mean_friend_count = mean(friend_count),
            median_friend_count = median(friend_count),
            n = n()) %>%
  ungroup() %>%
  arrange(age)

head(df.df_by_age_gender)


```

***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}
names(df.df_by_age_gender)
ggplot(data = df.df_by_age_gender, 
       aes(x = age, y = median_friend_count)) +
  geom_line(aes(color = gender))




```

***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:

***

### Reshaping Data
Notes:数据从长格式变成宽格式

```{r}
# install.packages('reshape2')
library(reshape2)
library(tidyr)

head(df.df_by_age_gender)

# reshape2(dcast:dataframe, acast:array,matrix)
df.df_by_age_gender.wide <- dcast(data = df.df_by_age_gender,
                                  age ~ gender,
                                  value.var = 'median_friend_count')

# df.df_by_age_gender.wide$ratio <- df.df_by_age_gender.wide$male / df.df_by_age_gender.wide$female
df.df_by_age_gender.wide$ratio <- with(data = df.df_by_age_gender.wide, male / female)

# tidyr(spread,gather)
df.df_by_age_gender.wide <-
  subset(df.df_by_age_gender[c('age','gender','median_friend_count')], !is.na(gender)) %>%
  spread(key = gender, value = median_friend_count) %>%
  mutate(ratio = male / female)


```


***

### Ratio Plot
Notes:

```{r Ratio Plot}
# The linetype parameter can take the values 0-6:
# 0 = blank, 1 = solid, 2 = dashed
# 3 = dotted, 4 = dotdash, 5 = longdash
# 6 = twodash

ggplot(data = df.df_by_age_gender.wide, aes(x = age, y = female / male)) +
  geom_line() +
  geom_hline(yintercept = 1, alpha = 0.3, linetype = 2) #进行一些图像的标注


```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}
df$year_joined <- floor(2014 - df$tenure/365)


```

***

### Cut a Variable
Notes:

```{r Cut a Variable}
summary(df$year_joined)
table(df$year_joined)
table(cut(df$year_joined, breaks = c(2004,2009,2011,2012,2014)))

df$year_joined.bucket <- cut(df$year_joined, breaks = c(2004,2009,2011,2012,2014))


```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}
ggplot(data = subset(df, !is.na(year_joined.bucket)), aes(x = age,y = friend_count)) +
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = median) 


```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}
ggplot(data = subset(df, !is.na(year_joined.bucket)), aes(x = age, y = friend_count)) +
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = mean) +
  geom_line(stat = 'summary', fun.y = mean, linetype = 2)  #是在上一条线的基础上进行操作所以会有均值


```

***

### Friending Rate
Notes:

```{r Friending Rate}
with(subset(df, tenure >= 1), summary(friend_count / tenure))


```

***

### Friendships Initiated
Notes:

What is the median friend rate?

What is the maximum friend rate?

```{r Friendships Initiated}
ggplot(data = subset(df, tenure >= 1), 
       aes(x = tenure, y = friendships_initiated / tenure)) + 
  geom_line(aes(color = year_joined.bucket))


ggplot(data = subset(df, tenure >= 1), 
       aes(x = tenure, y = friendships_initiated / tenure)) + 
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = mean)

# with(df, friendships_initiated / tenure)

```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(df, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(df, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(df, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(df, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)


ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(df, tenure >= 1)) +
  geom_smooth(aes(color = year_joined.bucket))


```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}
yo <- read.csv('yogurt.csv')
str(yo)

yo$id <- factor(yo$id)
str(yo)


ggplot(data = yo, aes(x = price)) +
  geom_histogram(fill = 'orange')


```

***

### Number of Purchases
Notes:

```{r Number of Purchases}
summary(yo$price)
length(unique(yo$price))
table(yo$price)

yo <- transform(yo, all.purchases = strawberry + blueberry + 
                  pina.colada + plain + mixed.berry)

qplot(data = yo, x = all.purchases)

qplot(data = yo, x = all.purchases, binwidth = 1, fill = 'orange')

```

***

### Prices over Time
Notes:

```{r Prices over Time}
ggplot(data = yo, aes(x = time, y = price)) + 
  geom_point(alpha = 1/4, position = 'jitter', shape = 21, fill = I('#f79420'))

ggplot(data = yo, aes(x = time, y = price)) + 
  geom_jitter(alpha = 1/4, shape = 21, fill = I('#f79420'))



```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}
set.seed(4230)
sample.ids <- sample(levels(yo$id), 16)

sample.ids

ggplot(aes(x = time, y = price), data = subset(yo, id %in% sample.ids)) + 
  facet_wrap(~id) +
  geom_line() +
  geom_point(aes(size = all.purchases), pch = 1)


```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:
```{r}
# install.packages("GGally")
library(GGally)
theme_set(theme_minimal(20))  #设置主题

set.seed(1836)
df_subset <- df[, c(2:7)]
names(df_subset)
ggpairs(df_subset[sample.int(nrow(df_subset), 1000), ])

ggpairs(df_subset[sample.int(nrow(df_subset), 1000), ], axisLabels = 'internal')

```

***

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
library(reshape2)
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

